Adaptative neighbouring methods applied to telephonic base stations

### 2024-08-22 article.tex

    This methods consists in multiple steps that can each be realised thanks to several methods that are compared : the $k$-NN method, the Delaunay triangulation or the Gabriel graph method are first used to create a first rough estimation of each point's neighbours. A filtering step is then applied in order to refine the neighbouring relationships that were found. This step is composed of several criteria that are successively being applied.

>>>>

    This methods consists in multiple steps that can each be realised thanks to several methods that are compared: the $k$-NN method, the Delaunay triangulation or the Gabriel graph method are first used to create a first rough estimation of each point's neighbours. A filtering step is then applied in order to refine the neighbouring relationships that were found. This step is composed of several criteria that are successively being applied.
